---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE
)
options(crayon.enabled = TRUE)
old_hooks <- fansi::set_knit_hooks(knitr::knit_hooks,
  which = c("output", "message", "error")
)

library(fs)
```

# Oddly Satisfying - Find delight in the mundane  

<!-- badges: start -->
<!-- badges: end -->

This repo contains slides and supporting materials for my presentation at the [2022 RStudio Conference](https://www.rstudio.com/conference/) in Washington D.C, July 28-29.  

> It happens to us all - a request to update a workflow or data started before your time. The materials left behind leave much to be desired; a few Word docs here, a couple Excel workbooks there, some scattered ArcGIS maps, and PDFs. But fear not! In this talk, we will cover how to complete a project intake by evaluating current workflows, data sources, and methods. Then, we will assess which tools to use, including packages like {groundhog}, {testthat}, and {rmarkdown} and version control with GitHub. We will cover code and file hygiene, and how to maintain your motivation when obstacles appear. Finally, we will explore strategies for making this legacy project your own and setting up the next round of updates for success. 

# Dates, logistics, requirements, etc.      

A _crisp_ 20 minutes.   

- Mid-June: schedule brown-bag style runthrough
- July 1: Have content mostly finalized 
- July 7: Deadline for outfit assembly, get haircut.  
- July 12: Speaker Coaching Content Review  
- July 21: Complete talk backup recording
- July 24: FLIGHT TO DC!
- July 25-27
    - Practice first thing in the morning, just before bed. 
    - Exercise, go to bed early, no sweets the morning of!

Contact person - Kim Goldsmith!!!

# Presentation  

Current plan is to use xaringan, but this might get difficult due to challenges with HTML styling. Backup is MS PowerPoint.  

This *shouldn't* have any actual tabular data, but we will see. 

I my previous experience with xaringinan makes me have some reservations about using it for this talk. This talk may rely heavily on screenshots and images. I also DREAD the constant scrolling up and down to get to each slide and the messy outline panel. 

This could potentially be remedied by modularization and clever `results='asis'` chunks.  

# Repo structure  

- `.\slides-reference.Rmd` is the standard xaringanthemer template. Will use for reference in `.\slides.Rmd`.  
- `.\css\` contains all CSS data, including font files, colors, etc. 
- `.\fig\` contains plots, screenshots, etc.  


```{r}
fs::dir_tree(recurse = F)
```

